---
title: "193DS_Final_Code"
author(s): Graycen Mahon, Benise Limon, Kiya ____ (sorry idk your last name!)
format: html
editor: visual
---

## Introduction:

For the first data set which is the study of the effects of Kangaroo Rat Mounds on Seed Banks of Grass
and Shrublands at the Sevilleta National Wildlife Refuge, New Mexico, we analyzed the data in order to answer the question, "How does the total seed number differ between kangaroo rat mound locations?". 

## Data Wrangling and Organization (Question 2 - seed count VS inflorescences):

```{r knitr-example, eval = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
# suppress any messages from R using the code chunk above, setting messages and warnings to false}
```

```{r organizing-files-using-the-here-package}
# I always get this wrong so maybe someone else should do it lol and I will copy it
```

```{r loading-in-packages}
library(tidyverse)
library(here)
library(janitor)
library(ggeffects)
library(performance)
library(naniar) 
library(flextable)
library(car)
library(broom)
library(corrplot)
library(AICcmodavg)
library(GGally)
```

## Question 2:  How does seed count vary with plot type (shrub or open), plant species, and total number of inflorescences? Is there a simpler model that explains seed count, and if so, what is it?

```{r reading-in-the-dataset}
individual_flower_data2 <- read_csv("shrubstudy_individual_flower_counts.ms.data.csv")
pollinator_data2 <- read_csv("shrubstudy_pollinator.ms.data.csv")
seed_data2 <- read_csv("shrubstudy_seed_ctwt.ms.data.csv")
community_flower_data2 <- read_csv("shrubstudy_community_flower_counts.ms.data.csv")
```

```{r missing-data-visualization-(1-4)}
gg_miss_var(individual_flower_data2)
gg_miss_var(pollinator_data2)
gg_miss_var(seed_data2)
gg_miss_var(community_flower_data2)
```

```{r}

```

