---
title: "test-code"
format: html
editor: visual
---
## Problem 1

```{r}
# Assuming 'counts' is a vector of count data
# Fit a Poisson regression model
krat_model <- glm(seeds ~ loc, family = poisson, data = krat_subset1)

# Extract the estimated dispersion parameter
dispersion <- summary(krat_model)$dispersion

# Check if the dispersion parameter is significantly greater than 1
if (dispersion > 1) {
  cat("Overdispersion detected (dispersion parameter =", dispersion, ")\n")
} else {
  cat("No evidence of overdispersion (dispersion parameter =", dispersion, ")\n")
}
```

```{r poisson-test}
poisson.test(1560, T = 4, r = 1,
    alternative = c("greater"),
    conf.level = 0.95)
```


```{r}
rpois(1560, lambda)
#Poisson Test

# Running a Kruskal-Wallis test to compare the seed count data for four different locations around the mounds 
```
poisson test attempt

overdispersion occurs when the variance of the counts is greater than the mean. In the Poisson distribution, the mean and variance are equal. To assess overdispersion, you can compare the sample variance to the sample mean. If the variance is significantly larger, it suggests overdispersion. In such cases, you may need to consider alternative models like negative binomial regression.

```{r}
# Assuming 'counts' is a vector of count data
# Fit a Poisson regression model
krat_model <- glm(seeds ~ loc, family = poisson, data = krat_subset1)

# Extract the estimated dispersion parameter
dispersion <- summary(krat_model)$dispersion

# Check if the dispersion parameter is significantly greater than 1
if (dispersion > 1) {
  cat("Overdispersion detected (dispersion parameter =", dispersion, ")\n")
} else {
  cat("No evidence of overdispersion (dispersion parameter =", dispersion, ")\n")
}
```

```{r}
# Assuming 'model' is the fitted Poisson regression model
# Calculate Pearson residuals
residuals <- residuals(krat_model, type = "pearson")

# Calculate the variance and mean of the residuals
variance <- var(residuals)
mean_residuals <- mean(residuals)

# Check if the variance is larger than the mean
if (variance > mean_residuals) {
  cat("Overdispersion detected (variance =", variance, ", mean =", mean_residuals, ")\n")
} else {
  cat("No evidence of overdispersion (variance =", variance, ", mean =", mean_residuals, ")\n")
}
```


<<<<<<< HEAD
## problem two original attempt

=======
```{r}
poisson.test(1560, T = 4, r = 1,
    conf.level = 0.95)
```

end poisson test attempt

## Problem 2
```{r knitr-example, eval = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
# suppress any messages from R using the code chunk above, setting messages and warnings to false}
```

```{r reading-in-the-dataset}
#reading in the data sets for problem 2
seed <- read_csv(here("data/shrubstudy_seed_ctwt.ms.data.csv"))
```

```{r cleaning-the-data}
seed %>% 
  #cleaning names
  clean_names()
  #creating new dataframe with columns
seed_col <- seed %>% 
  #selecting columns to have in data frame
  select(species, treatment, nr_seeds, total_nr_infl)
```

```{r missing-data-visualization-(1-4)}
#visualizing miss data points in seeds dataset
gg_miss_var(seed) +
  labs(caption = "Missing Data in the Seed Dataset") +
  theme(plot.caption = element_text(hjust = 0.6))
```

```{r}
#creating a seed subset object and dropping na values from the table
seed_subset <- seed_col
seed_subset[is.na(seed_subset) | seed_subset == "Inf"] <- NA 
seed_subset <- seed_col %>% 
  drop_na(nr_seeds)

#visualize missing data
gg_miss_var(seed_subset) +
  labs(caption = "Missing Data in the Seed Subset") +
  theme(plot.caption = element_text(hjust = 0.6))
#seed_subset$nr_seeds = as.numeric(as.character(seed_subset$nr_seeds)) 

```

```{r null-and-full-models}
#null model assigns the value of the predicted variable, seeds, to 1 so it is being modeled as a function of a constant term
null <- lm(nr_seeds ~ 1, data = seed_subset)
#full models includes all variables to assess a linear relationship between each predictor variable and seeds
full <- lm(nr_seeds ~ species + total_nr_infl + treatment, data = seed_subset)
```

```{r}
#create linear model for null model, make all graphs fit into pone 
null_model <- lm(nr_seeds ~ 1, data = seed_subset)
par(mfrow = c(2, 2))
#plot full linear model
plot(full)
```

```{r}
#Shapiro-Wilk test 
check_normality(full)
#Breusch-Pagan test
check_heteroscedasticity(full)
```

```{r}
#create a new model taking the log of the relationship between total mass and species type
#full_log <- lm(log(nr_seeds + .000000000000000000000000000000001) ~ species + total_nr_infl + treatment, data = seed_subset)

full_log <- lm(log(nr_seeds + min(nr_seeds[nr_seeds > 0])) ~ species + total_nr_infl + treatment, data = seed_subset)

#plotting to visually assess normality and homoscedasticity, making all four graphs on one page
par(mfrow = c(2, 2))
#plot full graph
plot(full_log)
```

```{r}
#Shapiro-Wilk test 
check_normality(full_log)
#Breusch-Pagan test
check_heteroscedasticity(full_log)
```

```{r explore-data-species}
ggplot(data = seed_subset, aes(x = species, y = nr_seeds), na.rm = TRUE) + geom_col()
```

```{r explore-data-inflorescences}
ggplot(data = seed_subset, aes(x = total_nr_infl, y = nr_seeds), na.rm = TRUE) + geom_col()
```

```{r explore-data plot type}
ggplot(data = seed_subset, aes(x = treatment, y = nr_seeds), na.rm = TRUE) + geom_col()
```

```{r}
#storing our summary model as an object 
model_summary <- summary(full)
#storing ANOVA table as an object
model_anova <- anova(full)

#displaying results from summary using the model object
model_summary
model_anova
```

```{r}
#creating a table that summarizes the anova table 
model_anova_table <- tidy(model_anova) %>% 
    #rounding the statistics, sum of mean squares and sum of squares, to two digits
    mutate(across(sumsq:meansq, ~ round(.x, digits = 2))) %>% 
    #round the F-statistic value to have 2 digits
    mutate(statistic = round(statistic, digits = 2)) %>% 
    ##replace the p value with < 0.001 rather than a super small number
    mutate(p.value = case_when(p.value < 0.001 ~ "< 0.001")) %>% 
    #rename the length to be more proper
    mutate(term = case_when(term == "length" ~ "Length", TRUE ~ term)) %>% 
    #create a flex table object from the data frame
    flextable() %>% 
    # change the header labels to be meaningful??
    set_header_labels(df = "Degrees of Freedom", 
                    sumsq = "Sum of Squares",
                    meansq = "Mean Squares",
                    statistic = "F-statistic",
                    p.value = "P-value")

model_anova_table
```

```{r}
#creating a summary table
table <- tidy(model_summary, conf.int = TRUE, exponentiate = TRUE) %>% 
#change low p-values to .001, change all values to round to 3 digits using mutate function
  mutate(statistic = round(statistic, digits = 3)) %>%
  mutate(std.error = round(std.error, digits = 3)) %>%
  mutate(conf.low = round(conf.low, digits = 3)) %>%
  mutate(conf.high = round(conf.high, digits = 3)) %>%
  mutate(estimate = round(estimate, digits = 3)) %>%
  mutate(p.value = case_when(p.value < 0.001 ~ "< 0.001")) %>% 
#create flextable
  flextable() %>% 
#fitting table to viewer
  autofit()
#show table 
  table
```
## end of probem 2 attempt 1